working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-02-22 Manuscript_draft/Manuscript_draft.Rmd
methods changes

The study was conducted in a glasshouse at University of New England (Armidale, Australia) from November 2017 to March 2018. Rooms were temperature controlled depending on the requirements of the species with day and night temperature differences. The experimental design had species from three different families: Solanaceae, Brassicaceae and Convolvulaceae (**Table 1**). The different species of the study have different reproductive traits and different degree of relatedness where the reciprocal crossed between species allowed us to have multiple different scenarios of both traits and relatedness. Moreover, the species selected have fast life cycle and low structural flower complexity in order to perform the pollination treatments and grow the different species from seeds. For the purpose of the experiment all the species where considered as pollen recipient and as pollen donor (see interaction matrix, fig 2). Species were watered once or twice per day and fertilized weekly (NPK 23: 3.95: 14).

>>>>

The study was conducted in a glasshouse at University of New England (Armidale, Australia) from November 2017 to March 2018. Rooms were temperature controlled depending on the requirements of the species with day and night temperature differences. The experimental design had species from three different families: Solanaceae, Brassicaceae and Convolvulaceae (**Table 1**). The different species of the study have different reproductive traits and different degree of relatedness where the reciprocal crosses between species allowed us to have multiple different scenarios of both traits and relatedness. Moreover, the species selected have fast life cycle and low structural flower complexity in order to perform the pollination treatments and grow the different species from seeds. For the purpose of the experiment all the species where considered as pollen recipient and as pollen donor (see interaction matrix, fig 2). Species were watered once or twice per day and fertilized weekly (NPK 23: 3.95: 14).

### 2019-02-22 Manuscript_draft/Manuscript_draft.tex
methods changes

The study was conducted in a glasshouse at University of New England
(Armidale, Australia) from November 2017 to March 2018. Rooms were
temperature controlled depending on the requirements of the species with
day and night temperature differences. The experimental design had
species from three different families: Solanaceae, Brassicaceae and
Convolvulaceae (\textbf{Table 1}). The different species of the study
have different reproductive traits and different degree of relatedness
where the reciprocal crossed between species allowed us to have multiple
different scenarios of both traits and relatedness. Moreover, the
species selected have fast life cycle and low structural flower
complexity in order to perform the pollination treatments and grow the
different species from seeds. For the purpose of the experiment all the
species where considered as pollen recipient and as pollen donor (see
interaction matrix, fig 2). Species were watered once or twice per day
and fertilized weekly (NPK 23: 3.95: 14).

>>>>

The study was conducted in a glasshouse at University of New England
(Armidale, Australia) from November 2017 to March 2018. Rooms were
temperature controlled depending on the requirements of the species with
day and night temperature differences. The experimental design had
species from three different families: Solanaceae, Brassicaceae and
Convolvulaceae (\textbf{Table 1}). The different species of the study
have different reproductive traits and different degree of relatedness
where the reciprocal crosses between species allowed us to have multiple
different scenarios of both traits and relatedness. Moreover, the
species selected have fast life cycle and low structural flower
complexity in order to perform the pollination treatments and grow the
different species from seeds. For the purpose of the experiment all the
species where considered as pollen recipient and as pollen donor (see
interaction matrix, fig 2). Species were watered once or twice per day
and fertilized weekly (NPK 23: 3.95: 14).
